Multilevel regression models

### 2023-10-11 procesamiento/prod_analysis-models.Rmd
meeting patrick

# Models perceived isolation

```{r class-pinsolation}
if (!require("pacman")) install.packages("pacman") # instalar pacman
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled)
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"))
df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$class5 <- factor(df1$class5,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (I+II)"
                                           ))
df1$class6 <- factor(df1$class6,levels = c("Petty-bourgeoise (IVa+b+c)",
                                           "Routine non-manual (IIIa+b)",
                                           "Skilled manual workers and supv. (V+VI)",
                                           "Non-skilled manual workers (VIIa+b)",
                                           "Service class (II - lower grade)",
                                           "Service class (I - higher grade)" 
                                           ))
df1$pi_nteg<- rowMeans(df1[,c("pi_compa","pi_isola","pi_left")],na.rm = T)
sjlabelled::set_label(df1$pi_nteg) <- "Perceived social isolation"
df1$Q05pcm <- car::recode(df1$Q05pc,"1='Q01';2='Q02';3='Q03';4='Q04';5='Q05';NA='Missing'",
                          as.factor = T,
                          levels = c("Q01","Q02","Q03","Q04","Q05","Missing")) 
frq(df1$Q05pcm)
dfreg <- df1 %>% dplyr::select(redist,
                        class6,class3,class5,
                        # tr_inte,
                        # eindex,
                        # know_total,
                        homclass,
                        homclass_gc,
                        # homclass_s,homclass_w,
                        # prestige,
                        # diversity,
                        pi_nteg,
                        # isei_range,
                        # hindex_sta,
                        # hindex_10,
                        Q05pcm,
                        labst,
                        union,
                        # sstatus,
                        gini_disp,
                        gini_mkt,
                        # palmawd,
                        rgdpna,
                        # giniwb,
                        # giniwd,
                        ednum,female,agenum,country) %>% 
  mutate(logrgdpna=log(rgdpna)) %>% 
  # filter(country!=233) %>% 
  na.omit()
dim(dfreg)

dfreg$country <- sjlabelled::as_factor(dfreg$country)
base <- lmer(redist~1 + (1|country),data=dfreg);performance::icc(base)
demo <- lmer(redist~1 +female+agenum + labst + union + (1|country),data=dfreg)
homclass <- lmer(redist~1 + female+agenum + labst + union+  homclass + (1|country),data=dfreg)
class <- lmer(redist~1 +female+agenum + labst + union+ class3+ (1|country),data=dfreg)
class_status <- lmer(redist~1 +female+agenum + labst + union+ class3+ednum+ Q05pcm + (1|country),data=dfreg)
full <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
full_b <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm + (1|country),data=dfreg)
full_m <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1|country),data=dfreg)
full_m_rs <- lmer(redist~1 +female+agenum + labst + union+ class3 +ednum+pi_nteg +  Q05pcm +  gini_disp + logrgdpna + (1+pi_nteg|country),data=dfreg)

plot_model(full_m_rs,type = "re")
anova(full_m,full_m_rs)

# Interactions segregation x class
full_int1 <- lmer(redist~1 +female+agenum + pi_nteg*class3+ ednum + Q05pcm + (1|country),data=dfreg)
# full_int3 <- lmer(redist~1 +female+agenum + labst + union+ homclass+pi_nteg*class3+ pi_nteg+ ednum + Q05pcm + tr_inte + (1|country),data=dfreg)

# Conditional Marginal effect
interplot <- 
interplot::interplot(m = full_int1,var1 = "pi_nteg",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Intermediate class (III+IV)","Service Class (I+II)","Working Class (V+VI+VII)")
df_int
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() +
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  ylab("Perceived Isolation coefficient")+
  xlab("Social Class")+
  ggtitle("Government's responsibility: reduce the differences in income between people with high incomes and those with low incomes") +
  geom_hline(yintercept = 0) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +  
  theme(plot.title = element_text(size = 8))

ggsave(plot = last_plot(),filename = "mar_pisolation_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

pred_data %>% 
ggplot() +
  geom_point(aes(x = x,y = predicted)) +
  geom_line(aes(x = x,y = predicted))+
  geom_errorbar(aes(x = x, ymin = conf.low, ymax = conf.high),color="black",width=0.05,size=1) +
  facet_grid(. ~ group) +
  labs(caption = paste0("N=",nobs(full),", Countries=",lme4::ngrps(full))) +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") + 
  theme_minimal()

ggsave(plot = last_plot(),filename = "pred_pisolation_class.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 10)

@@

```{r pinsolation-macro}
# Interactions segregation x inequality
df1$pi_isola_gc <- MLMusingR::group_center(df1$pi_isola,df1$country) 
df1$logrgdpna=log(df1$rgdpna)
df1$ratio10_50 <- df1$pc10_2017/df1$pc50_2017

df1$homclass

int_ginidis<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_disp+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_ginimkt <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini_mkt+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_palma <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*palmawd+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_pc10 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc10_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_pc50 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*pc50_2017+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_r1090 <- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*ratio10_50+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)
int_giniot<- lmer(redist~1 +female+agenum + labst + union+ class3 + homclass+pi_isola_gc*gini+ednum + Q05pcm  +logrgdpna + (1+pi_isola_gc|country),data=df1)

library(gridExtra)
p1<- interplot::interplot(m = int_ginidis,var1 = "pi_isola_gc",var2="gini_disp")+
  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)
p1$data$fake[p1$data$ub>0]
min(p1$data$fake[p1$data$ub>0])
max(p1$data$fake[p1$data$ub>0])

p2<- interplot::interplot(m = int_ginimkt,var1 = "pi_isola_gc",var2="gini_mkt") +
  xlab("Gini market") +geom_point()+ geom_hline(yintercept = 0)

p3<- interplot::interplot(m = int_palma,var1 = "pi_isola_gc",var2="palmawd") +
  xlab("Palma ratio (90/40)") + geom_point()+ geom_hline(yintercept = 0)

p4<- interplot::interplot(m = int_pc10,var1 = "pi_isola_gc",var2="pc10_2017") +
  xlab("Share GDP top 10%") + geom_point()+ geom_hline(yintercept = 0)

p5<- interplot::interplot(m = int_pc50,var1 = "pi_isola_gc",var2="pc50_2017") +
  xlab("Share GDP bottom 50%") + geom_point()+ geom_hline(yintercept = 0)

p6<- interplot::interplot(m = int_r1090,var1 = "pi_isola_gc",var2="ratio10_50") +
  xlab("Ratio (90/50)") + geom_point()+ geom_hline(yintercept = 0)

p7<- interplot::interplot(m = int_giniot,var1 = "pi_isola_gc",var2="gini") +
  xlab("Gini (WD)") + geom_point()+ geom_hline(yintercept = 0)

grid.arrange(p1,p2,p3,p4,p5,p6,nrow = 2)
g<- arrangeGrob(p1,p2,p3,p4,p5,p6,nrow = 2,top = "Perceived Isolation × Inequality")

ggsave(plot = g,filename = "mar_pisolation_ineq.png",device = "png",
       path = here::here("output"),width = 2,height = 1,units = "cm",scale = 20) 
```

@@

>>>>

## Perceived Isolation

```{r mod-isolation,results='asis', cache=T}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,class5,
                        homclass,
                        isolation,
                        Q05pcm,
                        Q03pcm,
                        # isei08,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears, 
                        female,
                        agenum,
                        country2,country,
                        union,
                        workst
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# dim(dfreg)

# lineal
base <- lmer(redist~1 + (1|country2),data=dfreg); icc1<- performance::icc(base)
class <- lmer(redist~ class3+ (1|country2),data=dfreg)
homclass <- lmer(redist~isolation + homclass + (1|country2),data=dfreg)
full1 <- lmer(redist~ class3 +isolation+homclass+female+agenum + age2+(1|country2),data=dfreg)
rob1 <- lmer(redist~class3+ isolation+homclass+ edyears+ female+ agenum+ age2+(1|country2),data=dfreg)
rob2 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ female+ agenum +age2+(1|country2),data=dfreg)
rob3 <- lmer(redist~class3+ isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+(1|country2),data=dfreg)
# Interactions segregation x class
int_homo <- lmer(redist~class3*isolation+homclass+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ (1|country2),data=dfreg)
# models <- list(homclass,class,full1,
#                # rob1,rob2,
#                rob4)
# texreg::screenreg(full1,single.row = F)

cap1 <- "Multilevel regression for redistributive preferences, social isolation and social class" 
coefgroup <- list("Social Class (ref: Service Class)"=2:3,
                  "Income Tercile (ref: Low)"=4:5,
                  "Isolation x Social Class"=9:10
                  )

coefmap <-  list(isolation ="Perceived Isolation",
                 'class3Intermediate class (III+IV)' ='Intermediate Class',
                 'class3Working Class (V+VI+VII)' ='Working Class',
                 "Q03pcmT02" = "Middle",
                 "Q03pcmT03" = "High",
                 "edyears" = 'Education in years',
                  "workstNot in paid work"="Not in labor force",
                 "unionYes" = 'Union membership: Yes',
                 'class3Intermediate class (III+IV):isolation'='Homogeneity x Intermediate Class',
                 'class3Working Class (V+VI+VII):isolation'='Homogeneity x Working Class',
                 # know_total="Number contacts"
                 # outgroup="Number outgroup"
                 homclass ="Class-based network homogeneity"
                 )

gofrow <-  list(Controls=c("No","No","No","Yes","Yes"))
gof1<-  c(NA,NA,"Num. Countries:","Var: Group",NA)

models <- list(homclass,class,full1,rob3,int_homo)
texreg::knitreg(models,caption=paste("(\\#tab:modredist)",cap1),caption.above=T,
                float.pos="h!",
                  include.thresholds=FALSE,
                  custom.coef.map=coefmap,
                  groups = coefgroup,
                  custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  custom.gof.names = gof1
                )

@@

```{r leverage2, eval=FALSE, include=FALSE}
pacman::p_load(influence.ME,lattice)
# dfbetas-----------------------------------------------------------------------
influence <- influence(rob3, "country2")
dfbetas(influence,parameters=c(1,4)) 
n_groups <- lme4::ngrps(rob3)

influence_est=as.data.frame(dfbetas(influence))
influence_est %>%  filter(homclass > 2/sqrt(n_groups))

plot(influence, which="dfbetas", 
     parameters=c("isolation"),
     xlab="DFbetaS", ylab="Country",cutoff = 2/sqrt(n_groups))

# cook-distance-----------------------------------------------------------------
# cooks.distance(rob3, sort = TRUE)
plot(influence, which="cook",
     cutoff=4/n_groups, sort=TRUE,
     xlab="Cooks Distance",
     ylab="Country")

sigtest1<- sigtest(influence, test=-1.96)
sigtest1$homclass
```

```{r marg2,fig.dim=c(4.1,2.6),fig.cap=c("Conditional marginal effects of Perceived Isolation on redistributive preferences"),out.width = "75%"}
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
# Conditional Marginal effect
interplot <- 
interplot::interplot(m = int_homo,var1 = "isolation",var2="class3")
df_int <- interplot$data
df_int <- df_int[c(1,2,4),]
df_int$value <- c("Service Class (I+II)","Intermediate class (III+IV)","Working Class (V+VI+VII)")
df_int$value <- factor(df_int$value,ordered = T,
                       levels = c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)"))

df_int %>% 
ggplot() + 
  geom_point(aes(x = value,y = coef1)) + 
  geom_errorbar(aes(x = value, ymin = lb, ymax = ub),color="black",width=0.1,size=1) +
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10))+
  ylab("Perceived Isolation")+
  xlab("Social Class")+
  ggtitle("Redistributive preferences") +
  geom_hline(yintercept = 0) + 
  labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(plot.title = element_text(size = 8))  
```

```{r pred2,fig.height=3.6,fig.width=5.7,fig.cap=c("Predictions for Redistributive Preferences"),out.width = '75%'}
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)       
# Predicted values 
plot_predictions(int_homo, condition = list("isolation","class3"),gray = F)+
  facet_grid(~factor(class3, levels=c("Working Class (V+VI+VII)","Intermediate class (III+IV)","Service Class (I+II)")))+
    labs(caption = paste0("N=",nobs(int_homo),", Countries=",lme4::ngrps(int_homo))) +
  theme(legend.position = "none")+ 
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences")
```

```{r mod-intermacro2,results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
df1$class3 <- relevel(df1$class3,ref =  "Intermediate class (III+IV)")
df1$labst1 <-car::recode(df1$labst,"'No information'='Not in labour force'")
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass,
                        isolation,
                        # homclass=eindex,
                        # homclass=ingroup,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        rgdpna,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        workst) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
  # filter(!country2 %in% c("Turkey","Estonia")) %>%
  na.omit()
# T03dim(dfreg)

main <- "redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2 +homclass"

giniD_gdp<-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(1|country2)")),data=dfreg)
giniD_rs <-lmer(formula(paste0(main,"+gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
# anova(giniD_gdp,giniD_rs)
giniD_int<- lmer(formula(paste0(main,"+isolation*gini_disp+logrgdpna","+(isolation|country2)")),data=dfreg)
# summary(giniD_int)

giniM_gdp<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1|country2),data=dfreg)
giniM_rs<- lmer(redist~class3+ isolation+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)
# anova(giniM_gdp,giniM_rs)
giniM_int <- lmer(redist~class3+ isolation*gini_mkt+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+ gini_mkt + logrgdpna+ (1+isolation|country2),data=dfreg)

models <- list(giniD_gdp,giniD_rs,giniD_int,
               giniM_gdp,giniM_rs,giniM_int)

texreg::knitreg(models,
                caption=paste("(\\#tab:modinter1)","Cross-level interaction for Perceived Isolation and Economic Inequality"),
                caption.above=T,
                  # include.thresholds=FALSE,
                  custom.coef.map=list(isolation="Perceived Isolation",
                                       logrgdpna="log GDP","gini_disp"="Gini (Disposable) ",
                                       "isolation:gini_disp"="Isolation x Gini (D)",
                                       "gini_mkt"="Gini (Market) ",
                                       "isolation:gini_mkt"="Isolation x Gini (M)",
                                       homclas="Class-based homogeneity"),
                  # groups = coefgroup,
                  # custom.gof.rows=gofrow,
                  include.loglik = FALSE,include.aic = FALSE,
                  # custom.gof.names = gof1
                )
```

```{r crosslevel2}
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,gridExtra)  
p1<- interplot::interplot(m = giniD_int,var1 = "isolation",var2="gini_disp")+
  ylab("Perceived Isolation coefficient")+ xlab("Gini disposable") +
  geom_point()+ geom_hline(yintercept = 0)

p2<- interplot::interplot(m = giniM_int,var1 = "isolation",var2="gini_mkt") +
  ylab("Perceived Isolation coefficient") + xlab("Gini market") +
  geom_point()+ geom_hline(yintercept = 0)

# Predicted values 
predval1 <- 
plot_predictions(giniD_int, condition = list("isolation",gini_disp=range),gray = T) +
  labs(caption = paste0("N=",nobs(giniD_int),", Countries=",lme4::ngrps(giniD_int)),
       linetype='Gini (Disposable)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

# Predicted values 
predval2 <- 
plot_predictions(giniM_int, condition = list("isolation",gini_mkt=range),gray = T)+
  labs(caption = paste0("N=",nobs(giniM_int),", Countries=",lme4::ngrps(giniM_int)),
       linetype='Gini (Market)') +
  xlab("Perceived Isolation")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")
```

```{r crossginiD2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Disposable)"),out.width='100%'}
grid.arrange(p1,predval1,nrow = 1    
             # Gini (Disposable)top = "Perceived Isolation × Gini (Disposable)"  
             )
```

```{r crossginiM2, fig.height=4,fig.width=9.3,fig.cap=c("Cross-level interaction for Perceived Isolation and Gini (Market)"),out.width='100%'}
grid.arrange(p2,predval2,nrow = 1    
             # top = "Perceived Isolation × Gini (Market)"  
             )
```

@@

## Gov's spending and individualism

```{r mod-spend-indv, results='asis'}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(dplyr,sjmisc,ggplot2,interplot,sjPlot,sjlabelled,haven,stringr,gridExtra)  
rm(list=ls())
load(here::here("input/data/proc/study1_country.RData"));df1 <- df2
dfreg <- df1 %>% dplyr::select(redist,
                        class3,
                        homclass=homclass_gc,
                        # homclass=homclass_res,
                        Q05pcm,
                        Q03pcm,
                        gini_disp,
                        gini_mkt,
                        giniot=gini,
                        giniindex,ttheilge1,
                        gv_spen=gv_spen,
                        top10,
                        middle50,
                        palmaratio,
                        d10d1,
                        rgdpna,
                        individualism,
                        edyears,
                        female,
                        agenum,
                        country2,
                        union,
                        workst
                        ) %>% 
  mutate(logrgdpna=log(rgdpna),
         age2=agenum^2,
         edyears2=edyears^2) %>%
    # filter(!country2 %in% c("Turkey","Estonia")) %>%
  # filter(MAINSTAT %in% c(1,2)) %>%
  # filter(agenum %in% c(25:65)) %>%
   na.omit()
int_indivi<- lmer(redist~class3+ homclass*individualism+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
int_govspe<- lmer(redist~class3+ homclass*gv_spen+ edyears+ Q03pcm+ workst+ union+ female+agenum +age2+logrgdpna + (1+homclass|country2),data=dfreg)
models_m <- list(int_indivi,int_govspe)
cap1=c("Cross-level interaction for Network homogeneity, Goverment Spending and Individualism")
customcoef <- 
list(homclass = "Class-based network homogeneity",
  logrgdpna           = "log GDP",
  individualism         = "Individualism Index*",
  "homclass:individualism" = "Homogeneity x Individualism",
  gv_spen               = "Gov. Spending (% GDP)*",
  "homclass:gv_spen"      = "Homogeneity x Gov. Spend."
)
texreg::knitreg(models_m,scalebox = 1,
                float.pos="h!",                
                custom.coef.map = customcoef,
                caption.above = T,caption = cap1)
```

```{r homclass-spend-indv, fig.height=6,fig.width=8,fig.cap=c("Cross-level interaction for Network homogeneity, Gov. Spending and Individualism"),out.width='100%',}
p8<- interplot::interplot(m = int_indivi,var1 = "homclass",var2="individualism") +
  xlab("Individualism Index*") + geom_point()+ geom_hline(yintercept = 0)+
  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)))

predval8 <- 
plot_predictions(int_indivi, condition = list("homclass",individualism=range),gray = F) +
  labs(caption = paste0("N=",nobs(int_indivi),", Countries=",lme4::ngrps(int_indivi)),
       linetype='Individualism') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

p9<- interplot::interplot(m = int_govspe,var1 = "homclass",var2="gv_spen") +
  xlab("Gov. Spending (% GDP)*") + geom_point()+ geom_hline(yintercept = 0)+
  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)))

predval9 <- 
plot_predictions(int_govspe, condition = list("homclass",gv_spen=range),gray = F) +
  labs(caption = paste0("N=",nobs(int_govspe),", Countries=",lme4::ngrps(int_govspe)),
       linetype='Gov.Spend') +
  xlab("Class-based homogeneity")+
  ylab("Redistributive preferences") +
  theme(legend.position = "right")

grid.arrange(p9,predval9,
             p8,predval8,nrow = 2)
```
